%----------------------------------------------------------------------------
% A bibtex még nem megy, addig is, jó lesz ez...
%----------------------------------------------------------------------------

\begin{thebibliography}{9}\addcontentsline{toc}{chapter}{Irodalomjegyzék}

%----------------------------- introduction -----------------------------
\bibitem{DuncanWatts} Duncan J. Watts, \emph {Networks, Dynamics, and the Small-World Phenomenom}.
American Journal of Sociology, Volume 105, Issue 2, 493-527. oldal, 1999.

\bibitem{DobreiMScOnlab1} Döbrei G., \emph {Nagyméretû hálózatok evolúciója - Trendterjedés vizsgálata szimulációs eszközökkel}.
Beszámoló, BME TMIT, Hálózatok és szolgáltatások, Önálló laboratórium 1., 2013.


%----------------------------- chatper 1. -----------------------------
\bibitem{Heuristics_for_Internet_Map_Discovery} Ramesh Govindan, Hongsuda Tangmunarunkit, \emph {Heuristics for Internet Map Discovery}.
INFOCOM 2000. Nineteenth Annual Joint Conference of the IEEE Computer and Communications Societies. Proceedings. IEEE Volume 3, 1371-1380. oldal, 2000.

\bibitem{Inferring_AS_level_Internet_Topology_from_Router_Level_Path_Traces} Hyunseok Chang, Sugih Jamin, Walter Willinger, \emph {Inferring AS-level Internet Topology from Router-Level Path Traces}.
In Proceedings of SPIE ITCom 2001, 2001.

\bibitem{On_Inferring_and_Characterizing_Internet_Routing_Policies} Feng Wang, \emph {On Inferring and Characterizing Internet Routing Policies}.
Proceeding IMC '03 Proceedings of the 3rd ACM SIGCOMM conference on Internet measurement, 15-26. oldal, 2003.

\bibitem{The_Impact_of_Routing_Policy_on_Internet_Paths} Hongsuda Tangmunarunkit, Ramesh Govindan, Scott Shenker, Deborah Estrin, \emph {The Impact of Routing Policy on Internet Paths}.
INFOCOM 2001. Twentieth Annual Joint Conference of the IEEE Computer and Communications Societies. Proceedings. IEEE Volume 2, 736-742. oldal, 2001.

\bibitem{Sobrinho_Algebra_and_Algorithms} J. L. Sobrinho, \emph {Algebra and Algorithms for QoS Path Computation and hop-by-hop Routing in the Internet}.
IEEE/ACM Transactions on Networking (TON), Volume 10., Issue 4, 541-550. oldal, 2002.

\bibitem{Compact_Policy_Routing} Rétvári G., Gulyás A., Heszberger Z., Csernai M., Biró J., \emph {Compact Policy Routing}.
Proceedings of the ACM Principles of Distributed Computing, 2011.

\bibitem{Sobrinho_Network_routing} J. L. Sobrinho, \emph {Network routing with path vector protocols: theory and applications}.
In SIGCOMM '03, 49-60. oldal, 2003.

\bibitem{Sobrinho_Metarouting} T. Griffin, J. L. Sobrinho, \emph {Metarouting}.
SIGCOMM '05, 1-12. oldal, 2005.

\bibitem{Lexicographic_products_in_metarouting} A. Gurney, T. Griffin, \emph {Lexicographic products in metarouting}.
In Network Protocols, IEEE International Conference on, 113-122. oldal, 2007.

\bibitem{Quality_of_service_routing_for_supporting_multimedia_applications} Zheng Wang, Jon Crowcroft, \emph {Quality-of-service routing for supporting multimedia applications}.
IEEE Journal of Selected Areas in Communications, Volume 14, Issue 7, 1228-1234. oldal, 1996.

\bibitem{Quality_of_service_based_routing_A_performance_perspective} G. Apostolopoulos, R. Guerin, S. Kamat, S. K. Tripathi, \emph {Quality of service based routing: A performance perspective}.
In SIGCOMM, 17-28. oldal, 1998.

\bibitem{On_path_selection_for_traffic_with_bandwidth_guarantees} Qingming Ma, P. Steenkiste, \emph {On path selection for traffic with bandwidth guarantees}.
In Proceedings of the 1997 International Conference on Network Protocols (ICNP '97), 191. oldal, 1997.

%----------------------------- chatper 2. -----------------------------
\bibitem{Routing_with_Guaranteed_Delivery_in_Adhoc_Wireless_Networks} P. Bose, P. Morin, I. Stojmenovic és J. Urrutia, \emph {Routing with Guaranteed Delivery in Ad-hoc Wireless Networks}.
Wireless Networks, Volume 7, Issue 6, 609-616. oldal, 2001.

%
%virusterjedes
%

\bibitem{Epidemic_Modelling_An_Introduction} D. J. Daley, J. Gani, \emph {Epidemic Modelling: An Introduction}.
Cambridge University Press, 2005.

\bibitem{Bernoulli_Blower} D. Bernoulli and S. Blower, \emph {An attempt at a new analysis of the mortality caused by smallpox and of the advantages of inoculation to prevent it}.
Reviews in Medical Virology, Volume 14, Issue 5, 275-288. oldal, 2004.

\bibitem{Contributions_to_the_mathematical_theory_of_epidemics} W. O. Kermack, A. G. McKendrick, \emph {Contributions to the mathematical theory of epidemics}.
Bulletin of Mathematical Biology, Volume 53, Issue 1, 33-55. oldal, 1927.

%
%trendterjedes
%

\bibitem{Csaba_Pal} Csaba Z. L., Pál J., \emph {Az utálat és az iskolai agresszió empirikus hálózatelemzése}.
VII. HUNNET konferencia, Budapesti Corvinus Egyetem, 2010.

\bibitem{The_Tipping_Point} M. Gladwell, \emph {Fordulópont: Ahol a kis különbségekbõl nagy változás lesz}.
HVG Kiadói Rt., 2007, ISBN: 9789639686007.

%
%internet
%
\bibitem{The_Internet_of_Things} D. Evans, \emph {The Internet of Things - How the Next Evolution of the Internet Is Changing Everything}.
Cisco Internet Business Solutions Group (IBSG), 2011.

\bibitem{DobreiBScSzakdolgozat} Döbrei G., \emph {Gráf-beágyazási technikák kommunikációs hálózatokban}.
BSc szakdolgozat, Budapesti Mûszaki és Gazdaságtudományi Egyetem, Távközlési és Médiainformatikai Tanszék, 2012.

\bibitem{Klein07} R. Kleinberg, \emph {Geographic Routing Using Hyperbolic Space}.
INFOCOM 2007. 26th IEEE International Conference on Computer Communications. IEEE, 1902-1909. oldal, 2007.

\bibitem{Thurston97} W. P. Thurston, \emph {Three-Dimensional Geometry and Topology}.
Princeton University Press, 1997.

\end{thebibliography}